Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-03-30 paper/AlignedIsotropicGW.tex
latexed an alpha

In Figure~\ref{fig:smallspinsalpha} we plot the evidence ratio of aligned to isotropic distributions (plotted as the equivalent sigma) with spin magnitudes given by this model with $\alpha$ in the range $0$ -- $6$. The top axis shows the mean spin magnitude
that value of alpha corresponds to (i.e., for the ``flat'' distribution $\alpha = 0$, the mean spin magnitude is 0.5). We see that if typical BH spins are $\lesssim 0.2$ we have no evidence for one model over the other.

>>>>

In Figure~\ref{fig:smallspinsalpha} we plot the evidence ratio of aligned to isotropic distributions (plotted as the equivalent sigma) with spin magnitudes given by this model with $\alpha$ in the range $0$ -- $6$. The top axis shows the mean spin magnitude
that value of $\alpha$ corresponds to (i.e., for the ``flat'' distribution $\alpha = 0$, the mean spin magnitude is 0.5). We see that if typical BH spins are $\lesssim 0.2$ we have no evidence for one model over the other.
